Benchmarks

### 2021-10-15 analysis/benchmarks.Rmd
refactor: increase figure width
refactor: reset figure width

---
title: "Benchmarks"
output:
  bookdown::html_document2:
    fig.width: 12
    fig.height: 8
---

@@

```{r benchmarks_plot_c_harrell}
autoplot(bmrk_results) +
    geom_boxplot(aes(fill = learner_id)) +
    geom_jitter(position = position_jitter(0.2)) +
    scale_fill_viridis(discrete = TRUE) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))
```

>>>>

---
title: "Benchmarks"
output:
  bookdown::html_document2:
    fig.width: 18
    fig.height: 8
---

@@

```{r benchmarks_plot_c_harrell, fig.width = 18}
autoplot(bmrk_results) +
    geom_boxplot(aes(fill = learner_id)) +
    geom_jitter(position = position_jitter(0.2)) +
    scale_fill_viridis(discrete = TRUE) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))
```
